Solutions to Integer Programming from Quantum Annealing

### 2020-09-13 paper/main.tex
edits

The graph $G(2)$ has the interesting feature of having a degenerate ground state depending on whether qubit 0 or 1 is chosen to be the MDS solution.
This degeneracy is reflected in the experimental result and provides a non-trivial benchmark for our simulation.
Fig.~\ref{fig:final_state_distribution} show the final state distribution of the three lowest lying state.
The states $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ are the two degenerate ground states of the embedded Hamiltonian, while $(1, 1, 1, 1, 1)$ is the first excited state which yields an incorrect solution.
All other states receive negligible probability at the end of annealing.
The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed. The asymmetry in the ground state distribution at non-zero offset is a result of annealing offsets lifting the ground state degeneracy.
Within the broken symmetry, the non-degenerate ground state switches between the two states depending on which qubit group is delayed. At zero offset, a slight asymmetry exists, and may be due to sampling bias~\cite{2016PhRvA..93e2320K, 2017PhRvL.118g0502M}.

>>>>

The graph $G(2)$ has the interesting feature of having a degenerate ground state depending on whether qubit 0 or 1 is chosen to be the MDS solution.
This degeneracy is reflected in the experimental result and provides a non-trivial benchmark for our simulation.
Fig.~\ref{fig:final_state_distribution} show the final state distribution of the three lowest lying state.
The states $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ are the two degenerate ground states of the embedded Hamiltonian, while $(1, 1, 1, 1, 1)$ is the first excited state which yields an incorrect solution.
All other states receive negligible probability at the end of annealing.
The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed. The asymmetry in the ground state distribution at non-zero offset is a result of annealing offsets lifting the ground state degeneracy.
Within the broken symmetry, the non-degenerate ground state switches between the two states depending on which qubit group is delayed. At zero offset, a slight asymmetry exists in the simulation because the Hamiltonian is only degenerate at the last moment, while the DWave is also subject to sampling bias~\cite{2016PhRvA..93e2320K, 2017PhRvL.118g0502M}.
